Multi-objective autotuning of MobileNets\\ across the full software/hardware stack

### 2018-06-01 dissemination.publication/08da9685582866a0/paper_appendix.tex
clean up

@@

\begin{packed_itemize}
  \item {\bf Live CK workflow:} \url{https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl}
  \item {\bf CK results:} \url{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-armcl-opencl}
  \item {\bf Artifact DOI:} \url{https://doi.org/10.1145/3229773}
  \item {\bf ReQuEST submission and reviewing guidelines:} \url{http://cknowledge.org/request-cfp-asplos2018.html} (\cite{request-asplos18})
  \item {\bf ReQuEST goals:} \cite{cm:29db2248aba45e59:0c7348dfbadd5b95}
  \item {\bf ReQuEST workflows:} \url{https://github.com/ctuning/ck-request-asplos18-results}
  \item {\bf ReQuEST scoreboard:} \url{http://cKnowledge.org/request-results}
\end{packed_itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Description}

\subsubsection{Artifact check-list}

@@

%-------------------------------------------------------------------------------
\subsubsection{How software can be obtained?}

>>>>

Submission and reviewing methodology: \\
{\em http://cTuning.org/ae/submission-20171101.html}

@@

\begin{packed_itemize}
  \item {\bf Latest CK workflow:} \url{https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl}
  \item {\bf CK results:} \url{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-armcl-opencl}
  \item {\bf Artifact DOI:} \url{https://doi.org/10.1145/3229773}
  \item {\bf ReQuEST submission and reviewing guidelines:} \url{http://cknowledge.org/request-cfp-asplos2018.html} (\cite{request-asplos18})
  \item {\bf ReQuEST goals:} \cite{cm:29db2248aba45e59:0c7348dfbadd5b95}
  \item {\bf ReQuEST workflows:} \url{https://github.com/ctuning/ck-request-asplos18-results}
  \item {\bf ReQuEST scoreboard:} \url{http://cKnowledge.org/request-results}
\end{packed_itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Artifact check-list}

@@

%-------------------------------------------------------------------------------
\subsection{Description}

\subsubsection{How to obtain}
